---
title: "esa_explore"
author: "Katherine Lauck"
date: '2022-08-04'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lubridate)
source("helper_functions.R")
```

```{r,echo=FALSE}
#t <- get_temp_data()
```

# Ideas for temp visualization
1. calculate time over 40 C - implemented in data fetching function (get_temp_data)
2. standardize each logger's max temp over the average max across all loggers per day (weighted to account for sample size differences)
3. regress max temp on day of year and plot residuals
4. regress time over 40 C on day of year and plot residuals

# Implement 2
```{r,echo=TRUE}
wmean <- t %>%
  group_by(date,habitat,logger_position) %>%
  summarize(meanmax = mean(max),n = n(),.groups = "keep") %>%
  ungroup(habitat) %>%
  summarize(wmean = weighted.mean(meanmax,n)) %>%
  right_join(t,by = c("date","logger_position")) %>%
  mutate(resid = max - wmean)
```
## Outside loggers
```{r,echo=TRUE}
filter(wmean,logger_position == "O") %>% ggplot(mapping = aes(x = habitat, y = resid)) +
  geom_boxplot() +
  xlab("Cover type") +
  ylab("Max temp standardized by daily max") +
  labs(title = "Outside loggers") +
  theme_classic()
```
```{r,echo=FALSE}
ggsave("../figures/max-weightedmean_outside.png",width = 6,height = 4)
```
```{r,echo=TRUE}
TukeyHSD(aov(resid~habitat, filter(wmean,logger_position == "O")),conf.level = .95)
```
## Inside loggers
```{r, echo=TRUE}
filter(wmean,logger_position == "I") %>% ggplot(mapping = aes(x = habitat, y = resid)) +
  geom_boxplot() +
  xlab("Cover type") +
  ylab("Max temp standardized by daily max") +
  labs(title = "Inside loggers") +
  theme_classic()
```
```{r, echo=FALSE}
ggsave("../figures/max-weightedmean_inside.png",width = 6,height = 4)
```
```{r, echo=TRUE}
TukeyHSD(aov(resid~habitat, filter(wmean,logger_position == "I")),conf.level = .95)
```
# Implement 3
```{r,echo=TRUE}
lmresid <- tibble(lmresid = resid(aov(max~yday(date),wmean)))
lmresid <- wmean %>% ungroup() %>% mutate(lmresid = pull(lmresid,lmresid))
```
## Outside loggers
```{r,echo=TRUE}
filter(lmresid,logger_position == "O") %>% ggplot(mapping = aes(x = habitat, y = lmresid)) +
  geom_boxplot() +
  xlab("Cover type") +
  ylab("Residual of max temp ~ day of year") +
  labs(title = "Outside loggers") +
  theme_classic()
```
```{r,echo=FALSE}
ggsave("../figures/resid_outside.png",width = 6,height = 4)
```
```{r,echo=TRUE}
TukeyHSD(aov(lmresid~habitat, filter(lmresid,logger_position == "O")),conf.level = .95)
```
## Inside loggers
```{r,echo=TRUE}
filter(lmresid,logger_position == "I") %>% ggplot(mapping = aes(x = habitat, y = lmresid)) +
  geom_boxplot() +
  xlab("Cover type") +
  ylab("Residual of max temp ~ day of year") +
  labs(title = "Inside loggers") +
  theme_classic()
```
```{r,echo=FALSE}
ggsave("../figures/resid_inside.png",width = 6,height = 4)
```
```{r,echo=TRUE}
TukeyHSD(aov(lmresid~habitat, filter(lmresid,logger_position == "I")),conf.level = .95)
```
# Implement 4
```{r,echo=TRUE}
resid40 <- tibble(resid40 = resid(aov(time_above_40~yday(date),lmresid)))
lmresid <- lmresid %>% mutate(resid40 = pull(resid40,resid40))
```
## Outside loggers
```{r,echo=TRUE}
filter(lmresid,logger_position == "O") %>% ggplot(mapping = aes(x = habitat, y = time_above_40)) +
  geom_boxplot() +
  xlab("Cover type") +
  ylab("Residual of time above 40C ~ day of year") +
  labs(title = "Outside loggers") +
  theme_classic()
```
```{r,echo=FALSE}
ggsave("../figures/resid_timeabove40_outside.png",width = 6,height = 4)
```
```{r,echo=TRUE}
TukeyHSD(aov(resid40~habitat, filter(lmresid,logger_position == "O")),conf.level = .95)
```
## Inside loggers
```{r,echo=TRUE}
filter(lmresid,logger_position == "I") %>% ggplot(mapping = aes(x = habitat, y = time_above_40)) +
  geom_boxplot() +
  xlab("Cover type") +
  ylab("Residual of time above 40C ~ day of year") +
  labs(title = "Inside loggers") +
  theme_classic()
```
```{r,echo=FALSE}
ggsave("../figures/resid_timeabove40_inside.png",width = 6,height = 4)
```
```{r,echo=TRUE}
TukeyHSD(aov(resid40~habitat, filter(lmresid,logger_position == "I")),conf.level = .95)
```
